%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Undergraduate Scientific Programmer} % Job title
    {Cohen Cognition and Perception Lab (CCPL)} % Organization
    {Wilmington, NC} % Location
    {Mar. 2016 - PRESENT} % Date(s)
    {
      \begin{cvitems}
        \item {Working in CCPL as part of a Directed Independent Study (DIS) at UNCW.}
        \item {Responsible for maintaining, developing, and documenting the lab's Java codebase.}
        \item {Designed and implemented procedures transitioning codebase to Git VCS.}
        \item {Transitioned development model to test-driven development to ensure more robust software.}
        \item {Created deployment procedures to minimize bad deployments.}
        \item {Deploying experiments to production server and ensuring correct configuration.}
      \end{cvitems}
    }
%%---------------------------------------------------------
  \cventry
    {Student Worker}
    %{Support Technician \& Project Coordinator \& Linux Subject Matter Expert (SME)} % Job title
    {UNCW Technology Assistance Center (TAC)} % Organization
    {Wilmington, NC} % Location
    {Aug. 2016 - PRESENT} % Date(s)
    {
      \begin{cvsubentries}
        \cvsubentry{}{Enterprise System Support (ESS) Project Coordinator}{Aug. 2017 - PRESENT}
        {
          \begin{cvsubitems}
            \item {Led a group of five TAC student workers.}
            \item {Assisted the UNCW ESS department with feedback of user facing services.}
          \end{cvsubitems}
        }
        \cvsubentry{}{Linux Subject Matter Expert (SME)}{Nov. 2016 - PRESENT}
        {
          \begin{cvsubitems}
            \item {Create documentation and ensure interoperability with Linux and UNCW services.}
            \item {Educate other members of TAC about how to troubleshoot Linux issues.}
            \item {Assist higher level support technicians in this domain.}
          \end{cvsubitems}
        }
        \cvsubentry{}{Support Technician}{Aug. 2016 - PRESENT}
        {
          \begin{cvsubitems}
            \item {Provide Tier 1 support for over 17,000 UNCW faculty, staff, and students.}
            \item {Streamline repetitive tasks such as cloud printing configuration for MacOS.}
          \end{cvsubitems}
        }
      \end{cvsubentries}
    }

%---------------------------------------------------------
%  \cventry
%    {Website Administrator Intern} % Job title
%    {AMS IT} % Organization
%    {Apex, NC} % Location
%    {Aug. 2013 - Jun. 2014} % Date
%    {
%      \begin{cvitems}
%        \item {Responsible for adding updated content.}
%        \item {Ensure consistent user experience.}
%        \item {Enforce cross-browser support and ADA compliance.}
%      \end{cvitems}
%    }
\end{cventries}
